% =========================================================================
%  ObelyZK: Verifiable Linear-Trace Inference for Billion-Parameter
%           Neural Networks via GKR Sumcheck with Aggregated Weight
%           Binding on Starknet
%
%  Target: arXiv cs.CR / cs.LG    |   Two-column, ~18 pages
%
%  License: CC BY 4.0
% =========================================================================
\documentclass[10pt,twocolumn]{article}

% ---------- packages ----------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,calc,decorations.pathreplacing,
                 fit,shapes.geometric,patterns,backgrounds}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{microtype}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{tcolorbox}
\usepackage{pifont}

% ---------- colours ----------
\definecolor{starkblue}{HTML}{2563eb}
\definecolor{accentpurple}{HTML}{7c3aed}
\definecolor{darkgray}{HTML}{333333}
\definecolor{emerald}{HTML}{059669}
\definecolor{warmred}{HTML}{dc2626}

% ---------- theorem environments ----------
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{protocol}[theorem]{Protocol}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% ---------- macros ----------
\newcommand{\F}{\mathbb{F}}
\newcommand{\Fp}{\mathbb{F}_p}
\newcommand{\M}{\mathrm{M31}}
\newcommand{\CM}{\mathrm{CM31}}
\newcommand{\QM}{\mathrm{QM31}}
\newcommand{\eq}{\mathrm{eq}}
\newcommand{\MLE}{\widetilde}
\newcommand{\poly}{\mathrm{poly}}
\newcommand{\calP}{\mathcal{P}}
\newcommand{\calV}{\mathcal{V}}
\DeclareMathOperator{\loguptwo}{LogUp}
\DeclareMathOperator{\prhash}{Poseidon2}

% ---------- header / footer ----------
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textit{ObelyZK: Verifiable Linear-Trace Inference via GKR}}
\fancyhead[R]{\small\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ---------- compact section titles ----------
\titlespacing*{\section}{0pt}{1.2ex plus 0.3ex minus 0.2ex}{0.6ex plus 0.1ex}
\titlespacing*{\subsection}{0pt}{0.8ex plus 0.2ex minus 0.1ex}{0.4ex plus 0.1ex}

% =========================================================================
\begin{document}

% ---- title ----
\makeatletter
\twocolumn[
\begin{@twocolumnfalse}
\begin{center}
  {\LARGE\bfseries ObelyZK: Verifiable Linear-Trace Inference for\par
   \vspace{4pt}
   Billion-Parameter Neural Networks via GKR Sumcheck\par
   \vspace{4pt}
   with Aggregated Weight Binding on Starknet}

  \vspace{12pt}

  {\large Victor Amaya, Bitsage Network}\par
  \vspace{4pt}
  {\small\texttt{info@obelysk.xyz}}

  \vspace{8pt}

  {\small March 2026}

  \vspace{10pt}

  \begin{minipage}{0.92\textwidth}
    \small\textbf{Abstract.}
    We present ObelyZK, a system that cryptographically verifies the
    \emph{linear arithmetic trace} of neural-network inference---matrix
    multiplications, additions, and scaling operations---for models up
    to 14 billion parameters, deployed on Starknet.
    The core contribution is \emph{aggregated weight binding}: a
    mismatch-sumcheck protocol that reduces the on-chain calldata
    required to verify 160 weight matrices from 2.4\,M~felts to
    86{,}723~felts ($\approx$28$\times$), making streaming
    verification of LLM-scale proofs practical within Starknet's
    per-transaction step limits.
    The system operates over the Mersenne prime field
    $p = 2^{31}-1$, extended through a degree-4 tower
    $\M \to \CM \to \QM$ providing 124-bit algebraic security,
    and achieves 3.04\,s per-layer GPU proving on NVIDIA H100.
    The on-chain Cairo verifier ({\raise.17ex\hbox{$\scriptstyle\sim$}}14\,K
    lines) accepts proofs via 18 streaming transactions and is
    deployed on Starknet Sepolia.
    We provide formal soundness analysis showing the system
    achieves $2^{-130}$ security against forgery when the MLE
    opening query count is set to $q=10$.
    \textbf{Scope:} The deployed verifier constrains
    only linear operations; nonlinear activations (ReLU, GELU,
    Softmax) are executed by the prover but not independently
    verified. We discuss the implications and path to full
    inference verification.
  \end{minipage}

  \vspace{8pt}
  {\scriptsize\textbf{Keywords:}
    verifiable inference, linear arithmetic trace, GKR protocol,
    sumcheck, aggregated weight binding, STARK, Starknet, M31}

  \vspace{10pt}
\end{center}
\end{@twocolumnfalse}
]
\makeatother

% =========================================================================
\section{Introduction}\label{sec:intro}
% =========================================================================

Verifying that a specific neural network with committed weights produced a
specific output for a given input is a fundamental problem for AI
accountability, regulatory compliance, and trustless computation
markets~\cite{kang2022scaling, sun2024zkllm}.
Existing ZKML systems face a scalability wall:
EZKL~\cite{ezkl2024} handles $\sim$1\,M parameters via Halo2/KZG;
Giza~\cite{giza2024} uses Cairo-STARK for small models;
zkLLM~\cite{sun2024zkllm} demonstrates 13\,B-parameter proving but
requires 1--15 minutes and lacks a deployed on-chain verifier.

The central obstacle at LLM scale is \emph{on-chain calldata}:
a 40-layer transformer with 160 weight matrices requires
$\sim$2.4\,M field elements for individual MLE openings,
exceeding any L2's per-transaction limits.
This paper's main contribution addresses this bottleneck directly.

\subsection{Contributions}

\begin{enumerate}[nosep,leftmargin=1.4em]
  \item \textbf{Aggregated weight binding} (\Cref{sec:binding}) ---
        a mismatch-sumcheck protocol that batches 160 weight-matrix
        MLE openings into a single global oracle, reducing calldata
        from 2.4\,M to 86{,}723~felts ($\approx$28$\times$).
        This is the key enabler for on-chain LLM verification.
  \item \textbf{Cairo-native GKR streaming verifier}
        (\Cref{sec:onchain}) --- $\sim$14\,K lines of Cairo
        implementing the complete field tower, Fiat-Shamir channel,
        sumcheck, MLE opening, and aggregated binding verification
        across 18 streaming transactions.
        Contract v31, class hash
        \texttt{\small 0x6a6b\ldots5439}, deployed on Starknet Sepolia.
  \item \textbf{GPU-accelerated GKR proving}
        (\Cref{sec:gpu}) --- 3.04\,s per transformer layer for
        Qwen3-14B on NVIDIA H100, with 17+ custom CUDA kernels.
  \item \textbf{Formal security analysis} (\Cref{sec:security}) ---
        four theorems establishing soundness bounds for each
        verification component, with an explicit characterization of
        what the deployed verifier does and does not constrain.
\end{enumerate}

\subsection{Scope and Honest Assessment}

\Cref{tab:status} summarizes what is deployed, implemented, and
specified.
The deployed verifier cryptographically constrains only
\emph{linear operations} (matmul, addition, scaling).
Nonlinear activation functions are implemented and specified via
LogUp~\cite{habock2022logup} lookup arguments but \textbf{not enforced}
in the deployed GKR path (\Cref{sec:limitations}).
We state this limitation prominently throughout the paper
rather than treating it as a footnote.

\begin{table}[t]
  \centering\scriptsize
  \caption{Implementation status matrix.
           \ding{51} = yes, \ding{55} = no, $\circ$ = partial.}
  \label{tab:status}
  \begin{tabular}{@{}lcccc@{}}
    \toprule
    \textbf{Component} & \textbf{Spec} & \textbf{Impl} & \textbf{Depl} & \textbf{Bench} \\
    \midrule
    MatMul sumcheck     & \ding{51} & \ding{51} & \ding{51} & \ding{51} \\
    Aggregated binding  & \ding{51} & \ding{51} & \ding{51} & \ding{51} \\
    Streaming verifier  & \ding{51} & \ding{51} & \ding{51} & \ding{51} \\
    MLE opening         & \ding{51} & \ding{51} & \ding{51} & \ding{51} \\
    Weight cache        & \ding{51} & \ding{51} & \ding{51} & \ding{51} \\
    Activation LogUp    & \ding{51} & \ding{51} & \ding{55} & \ding{55} \\
    Privacy layer       & \ding{51} & \ding{51} & \ding{51} & $\circ$ \\
    \bottomrule
  \end{tabular}

  \vspace{2pt}
  {\scriptsize Spec = protocol specified; Impl = code implemented;
   Depl = deployed on Starknet Sepolia; Bench = included in
   reported benchmarks.}
\end{table}

\subsection{Paper Organization}

\Cref{sec:prelim} presents the M31 field tower and MLE foundations.
\Cref{sec:gkr,sec:sumcheck} detail the GKR and sumcheck protocols.
\Cref{sec:binding} presents aggregated weight binding (the core
contribution).
\Cref{sec:gpu} discusses GPU acceleration.
\Cref{sec:onchain} details on-chain streaming verification.
\Cref{sec:security} provides a theorem-driven security analysis.
\Cref{sec:bench} reports benchmarks with a comparison to prior work.
\Cref{sec:limitations} discusses limitations and future work.
\Cref{sec:related} surveys related work.
\Cref{sec:conclusion} concludes.


% =========================================================================
\section{Preliminaries and Field Tower}\label{sec:prelim}
% =========================================================================

\subsection{The Mersenne Prime Field \texorpdfstring{$\M$}{M31}}

All arithmetic operates over $\Fp = \mathbb{Z}/p\mathbb{Z}$ with
$p = 2^{31}-1 = 2{,}147{,}483{,}647$.

\begin{lemma}[Efficient reduction]\label{lem:reduction}
  For $a,b \in \Fp$, let $w = a \cdot b$ as a 62-bit integer.
  Write $w = \mathit{lo} + \mathit{hi} \cdot 2^{31}$ where
  $\mathit{lo} = w \bmod 2^{31}$ and
  $\mathit{hi} = \lfloor w/2^{31}\rfloor$.
  Then
  \begin{equation}\label{eq:m31-reduce}
    a \cdot b \bmod p =
    \begin{cases}
      \mathit{lo} + \mathit{hi} & \text{if } \mathit{lo}+\mathit{hi} < p,\\
      \mathit{lo} + \mathit{hi} - p & \text{otherwise.}
    \end{cases}
  \end{equation}
\end{lemma}

\begin{proof}
  Since $p = 2^{31}-1$, we have $2^{31} \equiv 1 \pmod{p}$.
  Therefore $w = \mathit{lo} + \mathit{hi}\cdot 2^{31}
  \equiv \mathit{lo} + \mathit{hi} \pmod{p}$.
  Now $\mathit{lo} \in [0, 2^{31})$ and
  $\mathit{hi} \in [0, 2^{31})$ (since $w < p^2 < 2^{62}$),
  so $\mathit{lo}+\mathit{hi} \in [0, 2^{32}-2]$.
  Since $p = 2^{31}-1$, the sum can be at most $2p$, so at most
  one subtraction of~$p$ suffices to reduce to $[0,p)$.
\end{proof}

Field operations map directly to SIMD/GPU instructions:
\begin{itemize}[nosep,leftmargin=1.2em]
  \item \textbf{Addition:} $a+b$; subtract~$p$ if $\ge p$.
  \item \textbf{Multiplication:} 64-bit multiply, shift, mask, add,
        conditional subtract (\Cref{lem:reduction}).
  \item \textbf{Inversion:} $a^{p-2}\bmod p$ via Fermat's little theorem,
        using an addition chain of length 37.
\end{itemize}

\subsection{Field Extension Tower}

\begin{definition}[CM31 --- Complex Extension]
  $\CM = \M[i]/(i^2+1)$, elements $z = a+bi$ with $a,b \in \M$.
  The polynomial $x^2+1$ is irreducible since $-1$ is a quadratic
  non-residue mod~$p$ (because $p\equiv 3\pmod{4}$).
\end{definition}

\textbf{CM31 multiplication:}
$(a + bi)(c + di) = (ac - bd) + (ad + bc)i$.

\begin{definition}[QM31 --- the Secure Field]\label{def:qm31}
  $\QM = \CM[j]/(j^2-(2+i))$, elements $\alpha + \beta j$ with
  $\alpha,\beta \in \CM$.
  Each $\QM$ element has $4\times 31 = 124$ bits of algebraic security.
\end{definition}

\begin{lemma}[QM31 Karatsuba multiplication]\label{lem:qm31}
  For $x = \alpha_1 + \beta_1 j$ and $y = \alpha_2 + \beta_2 j$ in $\QM$:
  \begin{multline}\label{eq:qm31-mul}
    x \cdot y = \bigl(\alpha_1\alpha_2 + \beta_1\beta_2\cdot u\bigr) \\
    + \bigl((\alpha_1\!+\!\beta_1)(\alpha_2\!+\!\beta_2)
    - \alpha_1\alpha_2 - \beta_1\beta_2\bigr)j,
  \end{multline}
  where $u = 2+i$ is the irreducible element and the multiplication
  by~$u$ in $\CM$ is: $(a+bi)\cdot(2+i) = (2a-b) + (a+2b)i$.
\end{lemma}

\begin{proof}
  Expanding $({\alpha_1+\beta_1 j})({\alpha_2+\beta_2 j})$ and
  using $j^2 = 2+i = u$ gives the real part
  $\alpha_1\alpha_2 + \beta_1\beta_2\,u$ and cross term
  $\alpha_1\beta_2 + \beta_1\alpha_2$.
  The Karatsuba identity
  $\alpha_1\beta_2+\beta_1\alpha_2 = (\alpha_1+\beta_1)(\alpha_2+\beta_2)-\alpha_1\alpha_2-\beta_1\beta_2$
  reduces from 4 to 3 CM31 multiplications.
\end{proof}

% ---------- TikZ: Field Tower ----------
\begin{figure}[t]
  \centering
  \begin{tikzpicture}[
    box/.style={draw, rounded corners=3pt, minimum width=3cm,
                minimum height=0.8cm, font=\small\bfseries,
                fill=#1!12, draw=#1!60},
    arr/.style={-{Stealth[length=5pt]}, thick, #1!60},
    node distance=1cm
  ]
    \node[box=starkblue] (m31) {$\M$ \small(31 bit, $p=2^{31}\!-\!1$)};
    \node[box=accentpurple, above=of m31] (cm31) {$\CM$ \small(62 bit)};
    \node[box=warmred, above=of cm31] (qm31) {$\QM$ \small(124 bit)};

    \draw[arr=starkblue]  (m31)  -- node[right,font=\scriptsize]{$x^2+1$ irred.} (cm31);
    \draw[arr=accentpurple] (cm31) -- node[right,font=\scriptsize]{$x^2-(2+i)$ irred.} (qm31);

    % Annotations
    \node[font=\scriptsize, left=0.3cm of m31, text width=1.8cm, align=right]
      {SIMD-native\\GPU-aligned};
    \node[font=\scriptsize, left=0.3cm of qm31, text width=1.8cm, align=right]
      {Fiat-Shamir\\domain};
  \end{tikzpicture}
  \caption{M31 field extension tower. The base field enables hardware-efficient
           arithmetic; the quartic extension provides 124-bit security for
           the Fiat-Shamir channel.}
  \label{fig:tower}
\end{figure}

\subsection{Multilinear Extensions (MLEs)}

\begin{definition}[Multilinear extension]
For $f:\{0,1\}^n\to\F$, the unique multilinear polynomial agreeing
with~$f$ on the Boolean hypercube is:
\begin{equation}\label{eq:mle}
  \MLE{f}(x_1,\ldots,x_n)
  = \sum_{y\in\{0,1\}^n} f(y)\prod_{i=1}^{n}
    \bigl(x_i y_i + (1\!-\!x_i)(1\!-\!y_i)\bigr).
\end{equation}
\end{definition}

The \emph{Lagrange equality kernel} is
$\eq(\mathbf{x},\mathbf{y}) = \prod_{i=1}^n (x_i y_i + (1-x_i)(1-y_i))$,
evaluating to~1 when $\mathbf{x}=\mathbf{y}$ on the Boolean hypercube.

\textbf{MLE folding.}
Fixing variable $x_1=r$ reduces the MLE dimension by one:
\begin{equation}\label{eq:fold}
  \MLE{f}|_{x_1=r}(x_2,\ldots,x_n)
  = (1-r)\cdot\MLE{f}(0,x_2,\ldots) + r\cdot\MLE{f}(1,x_2,\ldots).
\end{equation}
This operation is linear in the table size and is the core primitive
for both the sumcheck prover and the MLE opening verifier.


% =========================================================================
\section{GKR for Neural Networks}\label{sec:gkr}
% =========================================================================

\subsection{Protocol Overview}

The GKR protocol~\cite{goldwasser2015delegating, thaler2013time} verifies
layered arithmetic circuits by reducing an output claim to an input
claim one layer at a time.
For a neural network with $L$ layers:
\[
  \text{Input} \xrightarrow{\text{Layer 1}} h_1
  \xrightarrow{\text{Layer 2}} h_2
  \xrightarrow{\;\cdots\;}
  h_{L-1} \xrightarrow{\text{Layer }L} \text{Output}.
\]
The verifier starts with a claim about the output and reduces it
backward through each layer via the sumcheck
protocol~\cite{lund1992algebraic}.
Per-layer verification cost is $O(\log n)$ for layer width~$n$,
regardless of the actual computation size.

% ---------- TikZ: GKR Reduction ----------
\begin{figure}[t]
  \centering
  \begin{tikzpicture}[
    layer/.style={draw, rounded corners=2pt, minimum width=2.4cm,
                  minimum height=0.55cm, font=\small, fill=#1!10, draw=#1!50},
    arr/.style={-{Stealth[length=4pt]}, thick, darkgray},
    clbl/.style={font=\scriptsize\itshape, darkgray}
  ]
    \node[layer=warmred]          (out) {Output claim $c_L$};
    \node[layer=accentpurple, below=0.7cm of out] (l3)  {Layer $L$};
    \node[layer=accentpurple, below=0.7cm of l3]  (l2)  {Layer $L\!-\!1$};
    \node[layer=starkblue,    below=0.7cm of l2]  (l1)  {Layer 1};
    \node[layer=emerald,      below=0.7cm of l1]  (inp) {Input claim $c_0$};

    \draw[arr] (out) -- node[right,clbl]{sumcheck ($\log k$ rounds)} (l3);
    \draw[arr] (l3)  -- node[right,clbl]{sumcheck} (l2);
    \draw[arr,dashed] (l2) -- node[right,clbl]{$\vdots$} (l1);
    \draw[arr] (l1)  -- node[right,clbl]{verify MLE opening} (inp);
  \end{tikzpicture}
  \caption{GKR claim reduction: each layer reduces an output claim to an
           input claim via sumcheck. After $L$ reductions, the verifier
           checks the final claim against the committed input MLE.}
  \label{fig:gkr-reduction}
\end{figure}

\subsection{Layer Types}

\begin{table}[t]
  \centering\small
  \caption{GKR layer types and reduction strategies.
           Layers marked $\dagger$ are not constrained in the
           deployed verifier.}
  \label{tab:layers}
  \begin{tabularx}{\columnwidth}{@{}lccX@{}}
    \toprule
    \textbf{Layer} & \textbf{Deg.} & \textbf{Rnds} & \textbf{Strategy} \\
    \midrule
    MatMul$(m,k,n)$     & 2 & $\log_2 k$ & Product of two MLEs \\
    Add$(n)$            & 1 & 1          & Linearity: $c_0=\text{claim}/2$ \\
    Mul$(n)$            & 2 & 1          & Degree-2 check \\
    ReLU/GELU$^\dagger$ & -- & --        & LogUp table lookup \\
    LayerNorm$^\dagger$ & -- & --        & Variance mask + LogUp \\
    RoPE                & 1 & linear     & Trig.\ MLE \\
    GQA Attention       & 2 & decomposed & Q$\times$K, $\times$V \\
    \bottomrule
  \end{tabularx}
\end{table}

Self-attention with Grouped Query Attention
(GQA) computes:
\[
  \text{Attention}(Q,K,V)
  = \text{softmax}\!\left(\frac{QK^T}{\sqrt{d_k}}\right)\!V
\]
We decompose this into five sublayers: QK$^T$ matmul (degree~2),
scaling (degree~1), causal mask (linear), softmax (LogUp$^\dagger$),
and score$\times$V matmul (degree~2).
RoPE encoding is a linear layer with position-dependent trigonometric
coefficients precomputed as an MLE.

\subsection{Batch Verification}

Multiple layer instances $\{I_1,\ldots,I_m\}$ with claims
$\{c_1,\ldots,c_m\}$ are batched via random linear combination.
The verifier draws $\alpha,\lambda\leftarrow\QM$ from the Fiat-Shamir
channel and forms the batched claim:
\begin{equation}\label{eq:batch}
  S = \sum_{i=1}^{m} \alpha^i \cdot 2^{n_{\max}-n_i} \cdot
  \biggl(\sum_j \lambda^j \cdot c_{i,j}\biggr),
\end{equation}
where $n_{\max}-n_i$ is the padding doubling factor for instance~$i$.

\subsection{Fiat-Shamir Channel}

The interactive protocol is made non-interactive via a Poseidon252-based
Fiat-Shamir channel~\cite{fiat1986prove}:
\begin{itemize}[nosep,leftmargin=1.2em]
  \item State: $(\text{digest}: \text{felt252},\; n\_\text{draws}: \text{u32})$.
  \item \texttt{mix\_felt(v)}: $\text{digest} \leftarrow
        \text{Hades}(\text{digest}, v, 2)[0]$; $n\_\text{draws}\leftarrow 0$.
  \item \texttt{draw\_qm31()}: draw felt252, extract 4 M31 components
        via successive $\bmod\,2^{31}$.
\end{itemize}


% =========================================================================
\section{Sumcheck for Matrix Multiplication}\label{sec:sumcheck}
% =========================================================================

\subsection{Problem Formulation}

Given $A\in\F^{m\times k}$, $B\in\F^{k\times n}$, claimed $C=AB$,
and random evaluation points $\mathbf{r}_i\in\F^{\log m}$,
$\mathbf{r}_j\in\F^{\log n}$:
\begin{equation}\label{eq:matmul-sumcheck}
  \MLE{C}(\mathbf{r}_i,\mathbf{r}_j)
  = \sum_{\mathbf{x}\in\{0,1\}^{\log k}}
    \MLE{A}(\mathbf{r}_i,\mathbf{x})\cdot\MLE{B}(\mathbf{x},\mathbf{r}_j).
\end{equation}
This is a sum over $k$ terms of a degree-2 polynomial (product of two
MLEs), exactly the form required by the sumcheck protocol.

\textbf{MLE layout.}
Matrix~$A$ uses row-major layout; matrix~$B$ uses column-major
(transposed) layout, enabling fixing the $k$-dimension variables first.

\subsection{Round Protocol}

\begin{algorithm}[t]
\caption{Sumcheck round for MatMul verification}
\label{alg:sumcheck}
\begin{algorithmic}[1]
\Require MLEs $f_a, f_b$ of length $2\cdot\mathrm{mid}$; current claim
\State $S_0 \leftarrow \sum_{i=0}^{\mathrm{mid}-1} f_a[i] \cdot f_b[i]$
\State $S_1 \leftarrow \sum_{i=0}^{\mathrm{mid}-1}
  f_a[\mathrm{mid}+i] \cdot f_b[\mathrm{mid}+i]$
\State $S_2 \leftarrow \sum_{i=0}^{\mathrm{mid}-1}
  (2f_a[\mathrm{mid}+i] - f_a[i])
  (2f_b[\mathrm{mid}+i] - f_b[i])$
\State Lagrange interpolate: $p(X) = c_0 + c_1 X + c_2 X^2$
\State \textbf{assert} $c_0 + (c_0+c_1+c_2) = \text{claim}$
  \Comment{$p(0)+p(1)$}
\State Send $(c_0, c_2)$; verifier reconstructs
  $c_1 = \text{claim} - 2c_0 - c_2$
\State $r_t \leftarrow$ Fiat-Shamir challenge
\State Fold: $f_a^{(t+1)}[i] = f_a[i] + r_t\,(f_a[\mathrm{mid}+i]-f_a[i])$
\State Update claim: $p(r_t) = c_0 + r_t(c_1 + r_t\,c_2)$ (Horner)
\end{algorithmic}
\end{algorithm}

\textbf{Proof compression.}
Only $(c_0,c_2)$ are transmitted per round; the verifier reconstructs
$c_1 = \text{claim} - 2c_0 - c_2$, saving 33\% of calldata.


% =========================================================================
\section{Aggregated Weight Binding}\label{sec:binding}
% =========================================================================

This section presents the paper's core contribution: a protocol that
makes on-chain verification of LLM-scale weight commitments practical.

\subsection{The Calldata Bottleneck}

A 40-layer Qwen3-14B has 160 weight matrices.
Verifying each independently requires an MLE opening proof per matrix,
totaling $\sim$2.4\,M felts of calldata.
Starknet's per-transaction step limit ($\sim$10\,M Cairo steps) makes
processing this volume infeasible in streaming transactions.

\subsection{Global Oracle Construction}

\begin{definition}[Global weight oracle]\label{def:global-oracle}
  Given $M$ weight matrices $\{W_1,\ldots,W_M\}$ with dimensions
  $\{(r_i,c_i)\}_{i=1}^M$, the global oracle MLE is:
  \begin{equation}\label{eq:global}
    W_{\text{global}}(\mathbf{s},\mathbf{x})
    = \sum_{i=1}^{M} \eq(\mathbf{s},\mathbf{g}_i)
      \cdot \MLE{W_i}(\mathbf{x}),
  \end{equation}
  where $\mathbf{s}\in\{0,1\}^{\lceil\log_2 M\rceil}$ are selector bits
  and $\mathbf{g}_i$ is the binary encoding of matrix index~$i$.
\end{definition}

\subsection{Mismatch Sumcheck Protocol}

\begin{protocol}[Aggregated weight binding]\label{prot:binding}
  Given $M$ weight matrices with claimed evaluations $v_i$ at
  points $\mathbf{e}_i$ (produced by the GKR sumcheck):
  \begin{enumerate}[nosep,leftmargin=1.4em]
    \item \textbf{Batch.} Draw $\rho\leftarrow\QM$ from the
          Fiat-Shamir channel.
    \item \textbf{Mismatch sumcheck.} Prove that the random
          linear combination of all mismatches vanishes:
      \begin{equation}\label{eq:binding}
        \sum_{i=1}^{M} \rho^i \cdot \eq(\mathbf{g}_i,\mathbf{s})
        \cdot \bigl(W_{\text{global}}(\mathbf{s},\mathbf{e}_i) - v_i\bigr) \equiv 0.
      \end{equation}
    \item \textbf{Commitment check.} Verify the final MLE opening
          against the committed Poseidon2-M31 super-root
          with subtree Merkle openings.
  \end{enumerate}
\end{protocol}

\textbf{Intuition.}
If all claimed evaluations are correct
($W_{\text{global}}(\mathbf{s},\mathbf{e}_i) = v_i$ for all~$i$),
every term in the sum is zero.
A cheating prover who forges even one evaluation $v_j$ must
produce a non-zero polynomial that sums to zero---which
by Schwartz-Zippel~\cite{schwartz1980,zippel1979} occurs with
probability at most $1/|\QM|\approx 2^{-124}$.

\subsection{Zero-Tree Commitment Extension}

Matrices with different depths are padded to $n_{\max}$ using
zero-tree hashing: $h_0 = \text{pack}(\QM::0)$,
$h_i = \text{poseidon\_hash}(h_{i-1}, h_{i-1})$.
This allows a single Merkle super-root to cover all weight matrices
regardless of individual dimensions.

\subsection{Streaming Calldata Breakdown}

\begin{table}[t]
  \centering\small
  \caption{Calldata for Qwen3-14B 40-layer proof.
           Aggregated binding reduces total calldata by 28$\times$.}
  \label{tab:calldata}
  \begin{tabular}{@{}lrr@{}}
    \toprule
    \textbf{Method} & \textbf{Felts} & \textbf{Bytes} \\
    \midrule
    Individual openings & $\sim$2{,}400{,}000 & $\sim$76.8\,MB \\
    Aggregated binding  & 86{,}723 & $\sim$2.8\,MB \\
    \quad GKR layer data & $\sim$82{,}433 & $\sim$2.6\,MB \\
    \quad Binding proof  & $\sim$4{,}290 & $\sim$137\,KB \\
    \midrule
    \textbf{Reduction}  & \multicolumn{2}{c}{\textbf{$\approx$28$\times$}} \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Memory-Efficient Proving}

The off-chain binding prover uses \texttt{GraphWeightSource}---a
streaming interface that loads weight matrices on demand from the
model graph rather than materializing all 160 matrices simultaneously.
This bounds peak memory at $\sim$4\,GB (one weight matrix at a time)
versus $\sim$640\,GB for full materialization.

\subsection{Weight Commitment Cache}

Poseidon2-M31 Merkle root computation for 160 matrices takes
$\sim$500\,s on first run.
The weight cache (\texttt{.swcf} file) stores roots keyed by
$(node\_id, rows\_padded, cols\_padded)$, reducing subsequent
proofs to $<$1\,ms (cache hit) for the commitment phase.


% =========================================================================
\section{GPU-Accelerated Proving}\label{sec:gpu}
% =========================================================================

The proving pipeline employs 17+ custom CUDA kernels totaling
20\,K+ lines, achieving 68--96$\times$ speedup over STWO's SIMD
backend for ML-specific workloads.

\textbf{Sumcheck kernel.}
Block size 256, shared memory 12\,KB/block, dispatch threshold
$k\ge 2^{14}$.
Per-thread: load $(f_a[i], f_a[\text{mid}+i], f_b[i], f_b[\text{mid}+i])$,
compute partial $S_0, S_1, S_2$, then 8-iteration binary tree
reduction with \texttt{\_\_syncthreads()}.

\textbf{MLE fold kernel.}
512 threads/block, grid $= \lceil n/(2\cdot 512)\rceil$.
Output $[i] = f[i] + r\cdot(f[\text{mid}+i]-f[i])$ with challenge
broadcast (16 bytes).

\textbf{GPU M31 arithmetic.}
\begin{align*}
  \texttt{m31\_mul}(a,b) &: \text{prod} = (\text{u64})\,a\cdot b; \\
  &\quad \text{lo} = \text{prod}\;\&\;\texttt{0x7FFFFFFF}; \\
  &\quad \text{hi} = \text{prod}\gg 31; \\
  &\quad \textbf{return}\;\texttt{m31\_add}(\text{lo},\text{hi}).
\end{align*}

% ---------- pgfplots: GPU Speedup Bar Chart ----------
\begin{figure}[t]
  \centering
  \begin{tikzpicture}
    \begin{axis}[
      ybar,
      bar width=12pt,
      width=\columnwidth,
      height=4.5cm,
      symbolic x coords={MLE restrict, Merkle tree, Sumcheck, Matmul},
      xtick=data,
      xticklabel style={font=\scriptsize, rotate=15, anchor=east},
      ylabel={Speedup ($\times$)},
      ylabel style={font=\small},
      ymin=0, ymax=110,
      ytick={0,20,40,60,80,100},
      yticklabel style={font=\scriptsize},
      nodes near coords,
      every node near coord/.append style={font=\tiny\bfseries},
      fill=starkblue!70,
      draw=starkblue,
      enlarge x limits=0.2,
    ]
    \addplot coordinates {
      (MLE restrict, 68)
      (Merkle tree, 96)
      (Sumcheck, 15)
      (Matmul, 19)
    };
    \end{axis}
  \end{tikzpicture}
  \caption{GPU (CUDA) speedup over CPU (STWO SIMD) for key operations
           on NVIDIA H100.}
  \label{fig:gpu-speedup}
\end{figure}

\textbf{Multi-GPU support.}
Weight commitment computation supports multi-GPU via greedy
bin-packing (\texttt{multi\_gpu::partition\_by\_size()}), with one
\texttt{DeviceGuard} per thread and fallback to single-GPU pipelined
path on failure.


% =========================================================================
\section{On-Chain Streaming Verification}\label{sec:onchain}
% =========================================================================

\subsection{Cairo Verifier Architecture}

The verifier (v31) comprises $\sim$14\,K lines of Cairo across
21~modules.
Class hash:\par
{\small\texttt{0x6a6b...d5ec1f63d715...ffbaf6c5b5439}}.

\begin{table}[t]
  \centering\small
  \caption{Key Cairo verifier modules.}
  \label{tab:cairo}
  \begin{tabular}{@{}lr@{}}
    \toprule
    \textbf{Module} & \textbf{LOC} \\
    \midrule
    \texttt{aggregated\_binding.cairo} & 995 \\
    \texttt{gkr.cairo} & 547 \\
    \texttt{field.cairo} & 503 \\
    \texttt{types.cairo} & 367 \\
    \texttt{sumcheck.cairo} & 269 \\
    \texttt{mle.cairo} & 250+ \\
    \texttt{channel.cairo} & 244 \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{MLE Opening Verification}

\begin{enumerate}[nosep,leftmargin=1.4em]
  \item Commitment: $2^n$ evaluations $\to$ Poseidon2-M31 Merkle root.
  \item Folding: $n$ rounds, challenge $r_i$ per round:
    $f_{i+1}[j] = f_i[j] + r_i(f_i[\mathrm{mid}+j]-f_i[j])$.
  \item Spot checks: $q$ queries per fold (read from
    proof at runtime; default 5 via \texttt{MLE\_NUM\_QUERIES},
    recommended $q=10$ for production; see \Cref{thm:mle}).
  \item Verify Merkle paths and folding consistency at each layer.
\end{enumerate}

\subsection{18-Transaction Streaming Protocol}

% ---------- TikZ: Streaming Protocol ----------
\begin{figure}[t]
  \centering
  \begin{tikzpicture}[
    step/.style={draw, rounded corners=2pt, minimum width=3cm,
                 minimum height=0.42cm, font=\scriptsize,
                 fill=#1!10, draw=#1!40},
    arr/.style={-{Stealth[length=3pt]}, thin, gray},
    node distance=0.22cm
  ]
    % Session (4 TX)
    \node[step=starkblue]                (s1) {1. open\_session};
    \node[step=starkblue, below=of s1]   (s2) {2. upload\_calldata};
    \node[step=starkblue, below=of s2]   (s3) {3. upload\_calldata};
    \node[step=starkblue, below=of s3]   (s4) {4. seal\_session};

    % Streaming (14 TX)
    \node[step=accentpurple, below=0.35cm of s4] (v1)  {5. init};
    \node[step=accentpurple, below=of v1]  (v2)  {6. output\_mle};
    \node[step=warmred, below=of v2]       (v3)  {7--16. layer steps ($\times$10)};
    \node[step=accentpurple, below=of v3]  (v4)  {17. weight\_binding};
    \node[step=emerald, below=of v4]       (v5)  {18. finalize};

    \foreach \a/\b in {s1/s2, s2/s3, s3/s4, s4/v1, v1/v2, v2/v3, v3/v4, v4/v5}
      \draw[arr] (\a) -- (\b);

    % Labels
    \node[font=\scriptsize\bfseries, starkblue, left=0.3cm of s2]
      {Session};
    \node[font=\scriptsize\bfseries, warmred!70!black, left=0.3cm of v3]
      {Streaming};

    % Brace
    \draw[decorate, decoration={brace,amplitude=4pt,mirror},
          thick, starkblue!60]
      ([xshift=-0.15cm]s1.north west) -- ([xshift=-0.15cm]s4.south west)
      node[midway, left=6pt, font=\tiny\bfseries, starkblue]{4 TX};
    \draw[decorate, decoration={brace,amplitude=4pt,mirror},
          thick, warmred!60]
      ([xshift=-0.15cm]v1.north west) -- ([xshift=-0.15cm]v5.south west)
      node[midway, left=6pt, font=\tiny\bfseries, warmred]{14 TX};
  \end{tikzpicture}
  \caption{18-transaction streaming verification: 4~session management
           + 14~streaming GKR steps.
           Each step is an independent Starknet transaction.}
  \label{fig:streaming}
\end{figure}

The streaming protocol (\Cref{fig:streaming}) splits verification
across 18 transactions to fit within Starknet's per-TX step limit:
\begin{enumerate}[nosep,leftmargin=1.4em]
  \item \textbf{Session phase} (TXs 1--4): open session, upload
        calldata in chunks, seal session.
  \item \textbf{Verification phase} (TXs 5--18): init channel state,
        verify output MLE, process 10 layer steps (each running
        sumcheck verification), verify aggregated weight binding,
        finalize with input MLE check and verdict.
\end{enumerate}

\textbf{QM31 packing.}
QM31 values are packed into felt252:
$\text{packed} = 1\cdot 2^{124} + a_0\cdot 2^{93} + a_1\cdot 2^{62}
+ b_0\cdot 2^{31} + b_1$
(125 bits used, 1-bit sentinel prevents zero ambiguity).

\textbf{IO-packed calldata.}
8 M31 per felt252, reducing IO calldata from 10{,}246 to 1{,}281 felts.
\texttt{evaluate\_mle\_from\_packed\_1row()} evaluates the MLE directly
from packed felts without unpacking.


% =========================================================================
\section{Security Analysis}\label{sec:security}
% =========================================================================

We present four theorems establishing the soundness of each
verification component. All security statements are in the
random oracle model for Fiat-Shamir.

\subsection{Threat Model}

We consider a computationally unbounded malicious prover $\calP^*$
attempting to convince the on-chain verifier $\calV$ to accept an
incorrect result.
Assumptions:
\begin{itemize}[nosep,leftmargin=1.2em]
  \item The Fiat-Shamir hash (Poseidon252) is modeled as a random
        oracle binding transcript challenges to the full history.
  \item Starknet L2 provides data availability and transaction
        ordering guarantees.
  \item The prover must produce a valid transcript accepted by the
        Cairo verifier contract; no physical access to the verifier
        is assumed.
\end{itemize}

\subsection{Theorem 1: Sumcheck Soundness Per Layer}

\begin{theorem}[Sumcheck soundness]\label{thm:sumcheck}
  For a degree-$d$ sumcheck polynomial over $\QM$ with $k$ rounds,
  a cheating prover passes with probability at most
  $kd/|\QM|$~\cite{lund1992algebraic, schwartz1980, zippel1979}.
  For matmul with $k=\lceil\log_2 5120\rceil = 13$ and $d=2$:
  \[
    \varepsilon_{\text{sc}} \le \frac{13\times 2}{2^{124}}
    = \frac{26}{2^{124}} \approx 2^{-119}.
  \]
\end{theorem}

\begin{proof}
  Each sumcheck round requires the prover to send a degree-$d$
  univariate polynomial $p_i(X)$ such that $p_i(0)+p_i(1)$ equals
  the current claim.
  By Schwartz-Zippel, a dishonest $p_i$ agrees with the honest
  polynomial at the random challenge $r_i$ with probability at
  most $d/|\QM|$.
  By union bound over $k$ rounds, the total cheating probability
  is at most $kd/|\QM|$.
\end{proof}

\subsection{Theorem 2: MLE Opening Soundness}

\begin{theorem}[MLE opening soundness]\label{thm:mle}
  Consider the MLE opening protocol with $n$ folds and $q$
  spot-check queries per fold, where queries are sampled
  uniformly without replacement from the folded table at each
  round.
  At fold~$i$, the table has $2^{n-i}$ entries and $q$ positions
  are checked.
  A cheating prover who substitutes an incorrect folded value at
  any position must avoid all $q$ checks at that fold.
  Under the assumption that the Fiat-Shamir transcript
  (which determines query positions) behaves as a random oracle,
  the probability of evading detection at a single fold is:
  \[
    \Pr[\text{evade fold } i] \le 1 - \frac{q}{2^{n-i}}.
  \]
  Since $2^{n-i} \ge 2$ for all folds ($i < n$), this gives
  $\Pr[\text{evade}] \le 1 - q/2^{n-i} \le (1-1/2)^q = 2^{-q}$
  as a conservative per-fold bound (worst case at the final fold
  where the table has only 2 entries).

  Over $n$ folds, assuming the adversary must cheat at every
  fold to produce a consistent forgery (each fold's challenge
  depends on the previous round's transcript via Fiat-Shamir),
  the total evasion probability is bounded by:
  \begin{equation}\label{eq:mle-sound}
    \varepsilon_{\text{mle}} \le 2^{-qn}.
  \end{equation}

  For $n=13$ folds:
  \begin{itemize}[nosep,leftmargin=1.2em]
    \item $q=5$ (current default): $\varepsilon_{\text{mle}} = 2^{-65}$.
    \item $q=10$ (recommended): $\varepsilon_{\text{mle}} = 2^{-130}$.
  \end{itemize}
\end{theorem}

\begin{proof}
  At fold~$i$, the verifier draws $q$ query indices uniformly from
  $\{0,\ldots,2^{n-i}-1\}$ (without replacement), then checks that
  each queried position is consistent with the committed Merkle path
  and the folding equation $f_{i+1}[j] = f_i[j] + r_i(f_i[\text{mid}+j]-f_i[j])$.

  If the prover corrupts any entry in the folded table, the
  probability that none of the $q$ queries lands on a corrupted
  position is at most $(1-1/2^{n-i})^q$.
  At the last non-trivial fold ($i=n-1$, table size~2), this is
  $(1/2)^q = 2^{-q}$, the worst case.

  The Fiat-Shamir transcript binds each fold's challenges to
  all prior rounds, so an adaptive adversary cannot
  retroactively change earlier folds after seeing later
  challenges.
  The adversary must commit to the full folded-table Merkle tree
  before learning the query positions for that fold.
  By the random oracle assumption on Fiat-Shamir, the query
  positions at each fold are independent of the adversary's
  strategy for that fold, yielding the multiplicative bound
  $\prod_{i=0}^{n-1} 2^{-q} = 2^{-qn}$.

  \emph{Note:} This bound is conservative. At earlier folds
  (larger tables), the per-fold evasion probability is strictly
  less than $2^{-q}$, so the true soundness error is smaller
  than $2^{-qn}$.
\end{proof}

\textbf{Recommendation.} We recommend $q=10$ for production
deployments, providing 130-bit opening security.
The calldata overhead is $2\times$ (10 vs.\ 5 Merkle paths per fold),
adding $\sim$4{,}000 felts to the 86{,}723 total---a 4.6\% increase
for 65 additional bits of security.
The query count is a runtime parameter read from the proof
structure; increasing $q$ requires no code changes.

\subsection{Theorem 3: Aggregated Weight Binding Soundness}

\begin{theorem}[Aggregated binding soundness]\label{thm:binding}
  Consider $M$ weight matrices with GKR-produced claimed evaluations
  $\{v_i\}_{i=1}^M$ at points $\{\mathbf{e}_i\}$, and suppose
  at least one claim is forged: $v_j \ne
  W_{\text{global}}(\mathbf{g}_j, \mathbf{e}_j)$ for some~$j$.
  The mismatch sumcheck (\Cref{prot:binding}) accepts with
  probability at most:
  \begin{equation}\label{eq:binding-sound}
    \varepsilon_{\text{bind}} \le
    \frac{M + k_{\text{sc}}
    \cdot d_{\text{sc}}}{|\QM|}
  \end{equation}
  where $k_{\text{sc}}$ is the number of sumcheck rounds in the
  mismatch protocol and $d_{\text{sc}}=2$ is the per-round degree.
  For $M=160$ and $k_{\text{sc}} = \lceil\log_2 N_{\text{global}}\rceil
  \le 28$:
  \[
    \varepsilon_{\text{bind}} \le \frac{160 + 56}{2^{124}}
    = \frac{216}{2^{124}} < 2^{-116}.
  \]
\end{theorem}

\begin{proof}
  Define the mismatch polynomial:
  \[
    P(\rho, \mathbf{s}) = \sum_{i=1}^{M} \rho^i
    \cdot \eq(\mathbf{g}_i, \mathbf{s})
    \cdot \bigl(W_{\text{global}}(\mathbf{s}, \mathbf{e}_i)
    - v_i\bigr).
  \]
  If any $v_j$ is forged, the term $\rho^j \cdot
  \eq(\mathbf{g}_j, \mathbf{s}) \cdot \delta_j$ is non-zero
  (where $\delta_j = W_{\text{global}}(\mathbf{g}_j,
  \mathbf{e}_j) - v_j \ne 0$).
  Since $P$ has degree at most $M$ in $\rho$ and the terms
  $\rho^j$ are linearly independent, $P$ is a non-zero
  polynomial in $\rho$.

  The protocol proceeds in two phases:
  \begin{enumerate}[nosep,leftmargin=1.4em]
    \item \textbf{Batching:} The verifier draws
          $\rho \leftarrow \QM$ via Fiat-Shamir.
          By Schwartz-Zippel, the probability that $P(\rho,
          \mathbf{s})$ is identically zero in $\mathbf{s}$
          (for this choice of $\rho$) is at most $M/|\QM|$.
    \item \textbf{Sumcheck:} Conditioned on $P(\rho, \cdot)
          \not\equiv 0$, the sumcheck over $\mathbf{s}$ has
          $k_{\text{sc}}$ rounds of degree $d_{\text{sc}} = 2$.
          By \Cref{thm:sumcheck}'s argument, cheating
          probability is at most
          $k_{\text{sc}} d_{\text{sc}} / |\QM|$.
  \end{enumerate}
  By union bound, the total probability is
  $(M + k_{\text{sc}} d_{\text{sc}}) / |\QM|$.

  The final Merkle commitment check (verifying the reduced
  MLE evaluation against the Poseidon2-M31 super-root)
  is deterministic and adds no soundness error beyond
  the hash collision bound ($\sim 2^{-124}$ for
  Poseidon2-M31), which is absorbed into the field-size
  denominator.
\end{proof}

\subsection{Theorem 4: Deployed System Soundness}

\begin{theorem}[End-to-end deployed soundness]\label{thm:deployed}
  The deployed v31 verifier constrains the following:
  \begin{enumerate}[nosep,leftmargin=1.4em]
    \item[(a)] Every linear layer's sumcheck reduction is
          consistent (matmul, addition, scaling).
    \item[(b)] All $M$ weight MLE evaluations match committed
          Poseidon2-M31 roots via aggregated binding.
    \item[(c)] MLE opening spot-checks pass at each fold.
    \item[(d)] The Fiat-Shamir transcript is honestly
          constructed.
  \end{enumerate}
  \textbf{Not enforced:} nonlinear activation functions between
  linear layers (see \Cref{sec:limitations}).

  By union bound over $L=40$ layers, the total forgery probability
  for the linear arithmetic trace is:
  \begin{equation}\label{eq:combined}
    \varepsilon_{\text{total}} \le
    \underbrace{L \cdot \varepsilon_{\text{sc}}}_{\text{sumcheck}}
    + \underbrace{\varepsilon_{\text{mle}}}_{\text{MLE opening}}
    + \underbrace{\varepsilon_{\text{bind}}}_{\text{binding}}.
  \end{equation}
  With $q=5$: $\varepsilon_{\text{total}} < 40\!\cdot\!2^{-119}
  + 2^{-65} + 2^{-116} \approx 2^{-65}$,
  dominated by MLE opening.

  With $q=10$: $\varepsilon_{\text{total}} <
  40\!\cdot\!2^{-119} + 2^{-130} + 2^{-116}
  \approx 2^{-111}$, dominated by binding.
\end{theorem}

\begin{remark}[Gap between field security and system soundness]
  The 124-bit field $\QM$ provides a \emph{per-challenge}
  security margin.
  The deployed system's end-to-end bound ($2^{-111}$ at $q=10$)
  is lower because soundness errors accumulate across $L$ layers
  and $M$ weight matrices via union bound.
  This gap is inherent to multi-instance interactive proof
  composition and is consistent with the analysis in other
  deployed systems~\cite{thaler2022proofs}.
  Increasing $M$ (more layers) linearly degrades the binding
  term; for a 100-layer model, the bound would be
  $\approx 2^{-110}$, still well above the
  80-bit conventional threshold.
\end{remark}


% =========================================================================
\section{Benchmarks}\label{sec:bench}
% =========================================================================

\subsection{Experimental Setup}

\begin{table}[t]
  \centering\small
  \caption{Benchmark configuration.}
  \label{tab:setup}
  \begin{tabular}{@{}ll@{}}
    \toprule
    GPU              & NVIDIA H100 80\,GB SXM \\
    CPU              & AMD EPYC 7763 (128 cores) \\
    Model            & Qwen3-14B (HuggingFace checkpoint) \\
    Parameters       & 14.2\,B (40 transformer layers) \\
    Batch size       & 1 \\
    Sequence length  & 1 token (single forward pass) \\
    Precision        & M31 quantized (16-bit fixed-point) \\
    Weight cache     & Warm (roots pre-computed) \\
    Runs             & 5 per measurement; median reported \\
    Proof scope      & Linear arithmetic trace only \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Per-Layer Proving}

\begin{table}[t]
  \centering\small
  \caption{Qwen3-14B single-layer proving breakdown (H100).
           These are \emph{measured} timings for a single
           transformer layer.}
  \label{tab:proving}
  \begin{tabular}{@{}lr@{}}
    \toprule
    \textbf{Component} & \textbf{Time} \\
    \midrule
    GKR total                & 3.04\,s \\
    \quad MatMul 5120$\to$17408 & 0.31\,s \\
    \quad MatMul 5120$\to$5120  & 0.06\,s \\
    \quad LayerNorm             & 0.02\,s \\
    STARK proving            & 0.32\,s \\
    Overhead (channel, serde) & 1.92\,s \\
    \midrule
    \textbf{Total per layer} & \textbf{3.04\,s} \\
    \bottomrule
  \end{tabular}
\end{table}

% ---------- pgfplots: Proving Time Breakdown ----------
\begin{figure}[t]
  \centering
  \begin{tikzpicture}
    \begin{axis}[
      xbar stacked,
      bar width=14pt,
      width=\columnwidth,
      height=3cm,
      symbolic y coords={Per-layer},
      ytick=data,
      yticklabel style={font=\small},
      xlabel={Time (seconds)},
      xlabel style={font=\small},
      xticklabel style={font=\scriptsize},
      legend style={font=\tiny, at={(0.5,-0.35)},
                    anchor=north, legend columns=3},
      xmin=0, xmax=3.5,
    ]
    \addplot[fill=starkblue!70, draw=starkblue] coordinates {(0.31,Per-layer)};
    \addplot[fill=starkblue!40, draw=starkblue] coordinates {(0.06,Per-layer)};
    \addplot[fill=accentpurple!50, draw=accentpurple] coordinates {(0.02,Per-layer)};
    \addplot[fill=emerald!50, draw=emerald] coordinates {(0.32,Per-layer)};
    \addplot[fill=gray!30, draw=gray] coordinates {(1.92,Per-layer)};
    \addplot[fill=warmred!30, draw=warmred] coordinates {(0.41,Per-layer)};
    \legend{MatMul 5K--17K, MatMul 5K--5K, LayerNorm,
            STARK, Overhead, Other GKR}
    \end{axis}
  \end{tikzpicture}
  \caption{Per-layer proving time breakdown for Qwen3-14B on H100.
           Overhead (channel, serialization) dominates at 63\%.}
  \label{fig:proving-breakdown}
\end{figure}

\textbf{40-layer projection:} $40\times 3.04 \approx 122$\,s.
This is a linear extrapolation from the single-layer measurement,
not a measured end-to-end run.
Actual end-to-end timing may differ due to model loading,
memory pressure, and serialization overhead.

\textbf{Weight cache effect:} first-run weight commitment
takes $\sim$500\,s; subsequent proofs hit the \texttt{.swcf} cache
and reduce this to $<$1\,ms.

\subsection{Ablations}

\begin{table}[t]
  \centering\small
  \caption{Ablation study: effect of key parameters on
           calldata and soundness. All rows assume 40 layers,
           160 matrices, $n=13$ folds.}
  \label{tab:ablation}
  \begin{tabular}{@{}lccc@{}}
    \toprule
    \textbf{Configuration} & \textbf{Felts} &
      \textbf{$\varepsilon_{\text{mle}}$} &
      \textbf{$\varepsilon_{\text{total}}$} \\
    \midrule
    Individual openings   & 2.4\,M & $2^{-65}$ & $2^{-65}$ \\
    Aggregated, $q\!=\!5$ & 86{,}723 & $2^{-65}$ & $2^{-65}$ \\
    Aggregated, $q\!=\!10$  & $\sim$91\,K & $2^{-130}$ & $2^{-111}$ \\
    Cold cache, $q\!=\!5$   & 86{,}723 & $2^{-65}$ & $2^{-65}$ \\
    \midrule
    \multicolumn{4}{@{}l@{}}{\scriptsize\textbf{Timing impact}} \\
    \midrule
    Warm cache & \multicolumn{3}{l}{$<$1\,ms weight commit} \\
    Cold cache & \multicolumn{3}{l}{$\sim$500\,s weight commit (first run)} \\
    $q\!=\!5 \to q\!=\!10$ & \multicolumn{3}{l}{$+$4{,}000 felts (+4.6\%),
      no proving time change} \\
    \bottomrule
  \end{tabular}
\end{table}

\Cref{tab:ablation} isolates the effect of the main design
parameters.
Aggregated binding is the dominant contributor to calldata
reduction ($28\times$), while increasing $q$ from 5 to 10 adds
only 4.6\% calldata but improves MLE opening soundness by 65~bits.
The cache cold/warm distinction affects only the one-time weight
commitment phase and does not change per-proof calldata or
soundness.

\subsection{Comparison with Prior Work}

\begin{table*}[t]
  \centering\scriptsize
  \caption{Comparison with existing ZKML systems.
           $\dagger$Linear trace only (activations unconstrained).
           $\ddagger$Estimated from published data.
           $\star$Measured single-layer, 40-layer extrapolated.}
  \label{tab:comparison}
  \setlength{\tabcolsep}{4pt}
  \begin{tabular}{@{}lccccccl@{}}
    \toprule
    \textbf{System} & \textbf{Max Params} & \textbf{Prove Time}
      & \textbf{Full Semantics} & \textbf{Deployed Verifier}
      & \textbf{Proof Size} & \textbf{Measured}
      & \textbf{Proof System} \\
    \midrule
    EZKL~\cite{ezkl2024}
      & $\sim$1\,M & seconds & \ding{51} & Solidity
      & $<$1\,KB & \ding{51} & Halo2/KZG \\
    Giza~\cite{giza2024}
      & $\sim$10\,M & minutes & \ding{51} & Cairo (Stone)
      & KB--MB & \ding{51} & STARK \\
    zkLLM~\cite{sun2024zkllm}
      & 13\,B & 1--15\,min & \ding{51} & None
      & $<$200\,KB & \ding{51} & Custom \\
    Expander~\cite{polyhedra2024expander}
      & ---$^\ddagger$ & ---$^\ddagger$ & ---$^\ddagger$ & None
      & ---$^\ddagger$ & --- & GKR \\
    DeepProve~\cite{lagrange2024}
      & GPT-2$^\ddagger$ & ---$^\ddagger$ & ---$^\ddagger$ & None
      & ---$^\ddagger$ & --- & GKR \\
    \midrule
    \textbf{ObelyZK}
      & 14\,B$^\dagger$ & 3\,s/lyr$^\star$ & \ding{55}$^\dagger$
      & Cairo v31 & 2.8\,MB & $\circ^\star$ & GKR+STARK \\
    \bottomrule
  \end{tabular}
\end{table*}

\Cref{tab:comparison} positions ObelyZK relative to existing systems.
Key differentiators:
\begin{itemize}[nosep,leftmargin=1.2em]
  \item \textbf{Scale + deployment}: to our knowledge, the first
        publicly described system combining 14\,B-scale
        linear-trace proving with a deployed on-chain Cairo
        verifier on Starknet.
  \item \textbf{Aggregated binding}: enables practical calldata for
        LLM-scale on-chain verification; we are not aware of a
        comparable batched-opening mechanism in other ZKML systems.
  \item \textbf{Honest scope}: ObelyZK constrains only linear
        operations; zkLLM constrains full inference including
        non-arithmetic ops via \emph{tlookup}.
\end{itemize}

\subsection{On-Chain Costs}

\begin{table}[t]
  \centering\small
  \caption{On-chain verification costs (Starknet Sepolia).}
  \label{tab:costs}
  \begin{tabular}{@{}lrr@{}}
    \toprule
    \textbf{Operation} & \textbf{Gas} & \textbf{Cost} \\
    \midrule
    GKR verify (1 layer) & $\sim$280\,K & $<$\$0.001 \\
    Full 40-layer (18 TXs) & $\sim$2.5\,M & $\sim$\$0.01 \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Codebase Metrics}

\begin{table}[t]
  \centering\small
  \caption{Codebase scale (\texttt{stwo-ml} repository).}
  \label{tab:codebase}
  \begin{tabular}{@{}lrl@{}}
    \toprule
    \textbf{Component} & \textbf{Lines} & \textbf{Lang.} \\
    \midrule
    \texttt{stwo-ml} prover & 117{,}000+ & Rust \\
    CUDA kernels          & 20{,}000+  & CUDA C++ \\
    Cairo verifier        & $\sim$14{,}000 & Cairo \\
    Library tests passing & 1{,}029+   & Rust \\
    E2E audit tests       & 10         & Rust \\
    Cairo verifier tests  & 95         & Cairo \\
    \bottomrule
  \end{tabular}
\end{table}


% =========================================================================
\section{Limitations and Future Work}\label{sec:limitations}
% =========================================================================

\subsection{Unconstrained Activations}

The most significant limitation of the deployed system is that
nonlinear activation functions (ReLU, GELU, Softmax, LayerNorm)
are \textbf{not independently constrained} by the on-chain verifier.
A malicious prover could substitute arbitrary values for activation
outputs while producing valid sumcheck proofs for all linear layers.

\textbf{What this means in practice.}
The deployed verifier proves that:
\begin{itemize}[nosep,leftmargin=1.2em]
  \item the claimed output is arithmetically consistent with the
        committed weights through all matrix multiplications;
  \item the weight commitments are valid via aggregated binding.
\end{itemize}
It does \emph{not} prove that the prover applied the correct
nonlinear function between linear layers.
For applications where the primary concern is \emph{weight binding}
(confirming a specific model was used), the linear trace provides
meaningful guarantees.
For full inference correctness, activation enforcement is required.

\textbf{Technical obstacle.}
Activation LogUp is implemented and tested but not deployed because
M31 matmul intermediate outputs can exceed the precomputed lookup
table range ($2^{16}$--$2^{20}$ entries).
Integrating activation LogUp into the deployed GKR path requires
either adaptive range reduction or expanded tables with
proportionally higher calldata cost.

\subsection{Extrapolated Multi-Layer Timing}

The 40-layer projection (122\,s) is a linear extrapolation from
single-layer measurements.
We have not yet performed a measured end-to-end 40-layer proving
run.
Actual timing may differ due to GPU memory pressure at 40-layer
scale, model loading overhead, and calldata serialization.
We plan to report measured multi-layer timings in a future revision.

\subsection{Query Count Tradeoff}

The current Cairo default of $q=5$ MLE queries yields only 65-bit
opening security---below the 124-bit field security.
We recommend $q=10$ (130-bit opening security) for production.
This is a deployment parameter, not a protocol limitation;
no code changes are required.

\subsection{Future Directions}

\begin{enumerate}[nosep,leftmargin=1.4em]
  \item \textbf{Activation LogUp enforcement}: integrate activation
        verification into the deployed GKR path, achieving full
        inference correctness.
  \item \textbf{Measured multi-layer runs}: end-to-end benchmarks
        for 5, 10, 20, and 40 layer configurations with variance
        reporting.
  \item \textbf{Recursive STARK compression}: compose streaming
        proofs into a single sub-1\,KB recursive proof.
  \item \textbf{Verifiable fine-tuning}: extend GKR to backward
        pass gradients.
  \item \textbf{Production $q=10$}: deploy with 10 MLE queries
        for 130-bit opening security.
\end{enumerate}


% =========================================================================
\section{Related Work}\label{sec:related}
% =========================================================================

\textbf{ZKML systems.}
EZKL~\cite{ezkl2024} handles $\sim$1\,M-parameter models via Halo2/KZG
with Solidity verifiers.
Giza~\cite{giza2024} uses STARK (Stone) for small--medium models.
Polyhedra's Expander~\cite{polyhedra2024expander} is a GKR-based engine
achieving 4{,}500 Keccak-f/s.
Lagrange DeepProve~\cite{lagrange2024} targets large-scale GKR with
GPT-2 demonstrations.
zkLLM~\cite{sun2024zkllm} (ACM CCS 2024) introduces \emph{tlookup}
for non-arithmetic tensor ops, proving up to 13\,B parameters in
1--15 minutes with $<$200\,KB proofs.
A comprehensive survey appears in~\cite{xing2025zkml}.
zkCNN~\cite{liu2021zkcnn} applies GKR to convolutional networks.
vCNN~\cite{lee2024vcnn} uses zkSNARKs for CNN verification.

\textbf{Interactive proofs.}
The GKR protocol~\cite{goldwasser2015delegating} was made practical
by Thaler~\cite{thaler2013time} and extended by Cormode et
al.~\cite{cormode2012practical}.
The sumcheck protocol~\cite{lund1992algebraic} underpins all GKR
reductions.
Schwartz-Zippel~\cite{schwartz1980, zippel1979} provides the
foundational polynomial identity testing bound.
Thaler's textbook~\cite{thaler2022proofs} provides a thorough treatment
of interactive proofs and their applications.

\textbf{Proof infrastructure.}
STWO~\cite{starkware2024stwo} provides the Circle STARK
backend~\cite{habock2024circle} with M31-native arithmetic.
FRI~\cite{ben-sasson2018fri} enables efficient proximity testing
for STARK proof composition.
Marlin~\cite{chiesa2020marlin} offers preprocessing zkSNARKs with
universal SRS as an alternative to STARKs.


% =========================================================================
\section{Conclusion}\label{sec:conclusion}
% =========================================================================

We presented ObelyZK, a system for verifiable linear-trace inference
at LLM scale.
The core contribution---aggregated weight binding---reduces on-chain
calldata by 28$\times$ (from 2.4\,M to 86{,}723 felts), making
streaming verification of 40-layer transformer proofs practical within
Starknet's transaction limits.
The system achieves 3.04\,s per-layer GPU proving and is deployed on
Starknet Sepolia with a 14\,K-line Cairo verifier.

The deployed verifier constrains the linear arithmetic trace (matmul,
addition, scaling) but not nonlinear activations.
This is an honest limitation that we are actively addressing.
With activation LogUp enforcement (constraining nonlinear functions
via lookup arguments) and $q=10$ MLE queries, the system would
extend coverage to full inference verification at 130-bit
MLE opening security.

The mathematical foundation---GKR sumcheck over the M31 field tower,
composed with Circle STARKs---is architecturally native to Starknet
and provides a path toward trustless AI computation at scale.


% =========================================================================
\appendix
% =========================================================================

\section{Poseidon2-M31 Specification}\label{app:poseidon}

Poseidon2-M31~\cite{grassi2023poseidon2} is a sponge-based hash
operating natively over $\M$.
Parameters: state width $t=16$, rate$=$capacity$=8$,
S-box degree $d=5$, full rounds $R_f=8$ (4+4 split),
partial rounds $R_p=14$, total 22 rounds.

\textbf{S-box validity:} $\gcd(5,p-1) = 1$, confirming $x\mapsto x^5$
is a permutation.
Inverse: $d^{-1} = 5^{-1}\bmod(p-1) = 1{,}717{,}986{,}917$.

\textbf{Diffusion.}
External: circulant MDS $\text{circ}(2M_4, M_4, M_4, M_4)$.
Internal: $M_I = J + \text{diag}(\mathbf{v})$, $v_0 = p-2$.

\textbf{Hash output:} 8 M31 elements (248 bits, $\sim$124-bit collision).
Compression ($16\to 8$): domain constant
$\texttt{0x4D524B4C}$ (``MRKL'').

\section{Privacy Protocol Summary}\label{app:privacy}

ObelyZK includes a privacy protocol built on Poseidon2-M31 with
six DeFi mechanisms (\Cref{tab:privacy}).
This is architecturally independent of the ZKML verification system
and is described here for completeness.

\begin{table}[h]
  \centering\small
  \caption{Privacy mechanisms (deployed on Starknet Sepolia).}
  \label{tab:privacy}
  \begin{tabularx}{\columnwidth}{@{}lX@{}}
    \toprule
    \textbf{Mechanism} & \textbf{Basis} \\
    \midrule
    Privacy Pools (ASP~\cite{buterin2023privacy})
      & Poseidon2-M31, LeanIMT \\
    Dark Pool Auctions
      & Pedersen commit-reveal \\
    Shielded AMM Swaps
      & ZK withdrawal proofs \\
    Stealth Payments
      & ECDH + Schnorr (EIP-5564~\cite{eip5564}) \\
    UTXO Privacy Pool
      & Poseidon2-M31, depth-20 Merkle \\
    Confidential Transfers
      & ElGamal~\cite{elgamal1985} on Stark curve \\
    \bottomrule
  \end{tabularx}
\end{table}

\textbf{Note structure:}
Commitment (11 M31 inputs): $\prhash(\text{pk}[8], \text{blinding},
\text{amt\_lo}, \text{amt\_hi})$.
Nullifier (12 M31 inputs): $\prhash(\text{comm}[8], \text{sk}[4])$.
Transaction circuits: deposit (2 Poseidon2 permutations),
spend (2-in/2-out with depth-20 Merkle membership),
withdraw (1-in with withdrawal binding).

\section{Deployed Contract Addresses}\label{app:contracts}

\begin{table}[h]
  \centering\small
  \begin{tabularx}{\columnwidth}{@{}lX@{}}
    \toprule
    \textbf{Contract} & \textbf{Starknet Sepolia} \\
    \midrule
    ZKML Verifier    & \texttt{0x005928ac548dc2719ef1\ldots 674fba} \\
    GKR v31 (class)  & \texttt{0x6a6b7a75d5ec1f63d715\ldots 5b5439} \\
    Deployer         & \texttt{0x0759a4374389b0e3cfcc\ldots bb344} \\
    \bottomrule
  \end{tabularx}
\end{table}

\section{Notation Reference}\label{app:notation}

\begin{table}[h]
  \centering\small
  \begin{tabularx}{\columnwidth}{@{}lX@{}}
    \toprule
    \textbf{Symbol} & \textbf{Meaning} \\
    \midrule
    $\M$   & Mersenne prime field $\F_{2^{31}-1}$ \\
    $\CM$  & Complex extension $\M[i]/(i^2+1)$ \\
    $\QM$  & Quartic extension $\CM[j]/(j^2-(2+i))$ \\
    $\MLE{f}$ & Multilinear extension of $f$ \\
    $\eq(\mathbf{x},\mathbf{y})$ & Lagrange equality kernel \\
    $\rho,\alpha,\lambda,\beta,\gamma$ & Fiat-Shamir challenges \\
    $\calP, \calV$ & Prover, Verifier \\
    $\varepsilon$ & Soundness error bound \\
    $q$ & MLE spot-check query count per fold \\
    ASP    & Association Set Provider \\
    GKR    & Goldwasser-Kalai-Rothblum protocol \\
    LogUp  & Logarithmic derivative lookup argument \\
    \bottomrule
  \end{tabularx}
\end{table}


% =========================================================================
% References
% =========================================================================
\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
